\bf A Comparision of Bootstrap Confidence Interval Methods

### 2022-12-06 project/PaperTemplate/paper.tex
Knitted to pdf

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{findCIs }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sampleinput, nboot) \{}

\NormalTok{  sample\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ sampleinput)}
\NormalTok{  sample\_sd }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ sampleinput)}
\NormalTok{  sample\_n }\OtherTok{\textless{}{-}} \FunctionTok{nrow}\NormalTok{(sampleinput)}
\NormalTok{  sample\_se }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sd}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(sample\_n)}

\NormalTok{  alphalow }\OtherTok{\textless{}{-}} \FloatTok{0.025}
\NormalTok{  alphahigh }\OtherTok{\textless{}{-}} \FloatTok{0.975}

  \CommentTok{\#perform bootstrap}
\NormalTok{  mean }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
\NormalTok{  sd }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
\NormalTok{  se }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
\NormalTok{  t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}

  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{nboot) \{}
\NormalTok{    resampled }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mosaic}\SpecialCharTok{::}\FunctionTok{resample}\NormalTok{(sampleinput, }\AttributeTok{replace =} \ConstantTok{TRUE}\NormalTok{))}
\NormalTok{    mean[i] }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ resampled)}
\NormalTok{    sd[i] }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ X, }\AttributeTok{data =}\NormalTok{ resampled)}
\NormalTok{    se[i] }\OtherTok{\textless{}{-}}\NormalTok{ sd[i]}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(resampled))}
\NormalTok{    t\_stat[i] }\OtherTok{\textless{}{-}}\NormalTok{ (mean[i] }\SpecialCharTok{{-}}\NormalTok{ sample\_mean)}\SpecialCharTok{/}\NormalTok{se[i]}
\NormalTok{  \}}

\NormalTok{  boot\_means }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mean)}
\NormalTok{  boot\_t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(t\_stat)}

  \CommentTok{\# find the standard confidence interval}
\NormalTok{  standard\_interval }\OtherTok{\textless{}{-}}\NormalTok{ sample\_mean }\SpecialCharTok{+} 
    \FunctionTok{qnorm}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)) }\SpecialCharTok{*}\NormalTok{ sample\_sd}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(sample\_n)}

  \CommentTok{\# find percentile interval}
\NormalTok{  percentile\_interval }\OtherTok{\textless{}{-}} \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{), }\AttributeTok{data =}\NormalTok{ boot\_means)}

  \CommentTok{\# find BC interval}
\NormalTok{  less\_than\_sample\_mean }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(}\FunctionTok{ifelse}\NormalTok{(boot\_means }\SpecialCharTok{\textless{}=}\NormalTok{ sample\_mean, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{))}\SpecialCharTok{/}\NormalTok{nboot}
\NormalTok{  z0 }\OtherTok{\textless{}{-}} \FunctionTok{qnorm}\NormalTok{(less\_than\_sample\_mean)}
\NormalTok{  newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}
\NormalTok{  newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(}\DecValTok{2}\SpecialCharTok{*}\NormalTok{z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}

\NormalTok{  bc\_interval }\OtherTok{\textless{}{-}} \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(newlow, newhigh), }\AttributeTok{data =}\NormalTok{ boot\_means)}

  \CommentTok{\# find BCa interval}
\NormalTok{  theta }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x)\{}\FunctionTok{mean}\NormalTok{(x)\}}
\NormalTok{  jackknife\_results }\OtherTok{\textless{}{-}}\NormalTok{ bootstrap}\SpecialCharTok{::}\FunctionTok{jackknife}\NormalTok{(sampleinput}\SpecialCharTok{$}\NormalTok{X, theta)}
\NormalTok{  jackmean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values)}
\NormalTok{  estimated\_a }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{1}\SpecialCharTok{/}\DecValTok{6}\NormalTok{)}\SpecialCharTok{*}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jackmean)}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{)}\SpecialCharTok{/}
\NormalTok{    (}\FunctionTok{sum}\NormalTok{((jackknife\_results}\SpecialCharTok{$}\NormalTok{jack.values }\SpecialCharTok{{-}}\NormalTok{ jackmean)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}\SpecialCharTok{\^{}}\NormalTok{(}\FloatTok{1.5}\NormalTok{)}
\NormalTok{  a\_newlow }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))}\SpecialCharTok{/}
\NormalTok{                      (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphalow))))}
\NormalTok{  a\_newhigh }\OtherTok{\textless{}{-}} \FunctionTok{pnorm}\NormalTok{(z0 }\SpecialCharTok{+}\NormalTok{ (z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))}\SpecialCharTok{/}
\NormalTok{                       (}\DecValTok{1}\SpecialCharTok{{-}}\NormalTok{estimated\_a}\SpecialCharTok{*}\NormalTok{(z0 }\SpecialCharTok{+} \FunctionTok{qnorm}\NormalTok{(alphahigh))))}
\NormalTok{  bca\_interval }\OtherTok{\textless{}{-}} \FunctionTok{qdata}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\FunctionTok{c}\NormalTok{(a\_newlow, a\_newhigh), }\AttributeTok{data =}\NormalTok{ boot\_means)}

  \CommentTok{\# find studentized interval}
\NormalTok{  t\_q }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{quantile}\NormalTok{(boot\_t\_stat}\SpecialCharTok{$}\NormalTok{t\_stat, }\FunctionTok{c}\NormalTok{(}\FloatTok{0.025}\NormalTok{, }\FloatTok{0.975}\NormalTok{)))}
\NormalTok{  lower\_q }\OtherTok{\textless{}{-}}\NormalTok{ t\_q[}\DecValTok{1}\NormalTok{]}
\NormalTok{  upper\_q }\OtherTok{\textless{}{-}}\NormalTok{ t\_q[}\DecValTok{2}\NormalTok{]}
\NormalTok{  t\_interval }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(sample\_mean }\SpecialCharTok{{-}}\NormalTok{ (upper\_q}\SpecialCharTok{*}\NormalTok{sample\_se), sample\_mean }\SpecialCharTok{{-}}\NormalTok{ (lower\_q}\SpecialCharTok{*}\NormalTok{sample\_se))}

\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(standard\_interval, percentile\_interval, bc\_interval, }
\NormalTok{                 bca\_interval, t\_interval)}
  \FunctionTok{names}\NormalTok{(output) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Standard Interval"}\NormalTok{, }\StringTok{"Percentile Interval"}\NormalTok{, }\StringTok{"BC Interval"}\NormalTok{, }
                     \StringTok{"BCa Interval"}\NormalTok{, }\StringTok{"Studentized Interval"}\NormalTok{)}
\NormalTok{  output}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{run\_simulation\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \DecValTok{0}

\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(sample\_sizes, }\AttributeTok{mean =} \DecValTok{0}\NormalTok{, }\AttributeTok{sd =} \DecValTok{1}\NormalTok{)}
\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
\NormalTok{  res}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{run\_simulation\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \DecValTok{4}

\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rgamma}\NormalTok{(sample\_sizes, }\AttributeTok{shape =} \DecValTok{1}\NormalTok{, }\AttributeTok{scale =} \DecValTok{4}\NormalTok{)}
\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
\NormalTok{  res}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{collect\_data\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{10}

  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_gamma, }
                        \AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps}

\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{+}\DecValTok{10}
\NormalTok{  \}}

\NormalTok{  gamma\_output }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(data2) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Standard"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"BC"} \OtherTok{=}\NormalTok{ V4, }
           \StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V6) }
\NormalTok{  gamma\_output}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{collect\_data\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{10}

  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_normal, }
                        \AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps)}

\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{+}\DecValTok{10}
\NormalTok{  \}}

\NormalTok{  normal\_output }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(data2) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Standard"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"BC"} \OtherTok{=}\NormalTok{ V4, }
           \StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V6) }
\NormalTok{  normal\_output}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
\NormalTok{sim\_reps }\OtherTok{\textless{}{-}} \DecValTok{10000}

\NormalTok{gamma\_data }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_gamma}\NormalTok{(sim\_reps)}
\FunctionTok{write.csv}\NormalTok{(gamma\_data1,}\StringTok{"gamma\_data1.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}

\NormalTok{normal\_data }\OtherTok{\textless{}{-}} \FunctionTok{collect\_data\_normal}\NormalTok{(sim\_reps)}
\FunctionTok{write.csv}\NormalTok{(normal\_data1,}\StringTok{"normal\_data1.csv"}\NormalTok{, }\AttributeTok{row.names =} \ConstantTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{gamma\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}gamma\_data1\_10000.csv\textquotesingle{}}\NormalTok{)}
\NormalTok{normal\_df }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\AttributeTok{file =} \StringTok{\textquotesingle{}normal\_data1\_10000.csv\textquotesingle{}}\NormalTok{)}

>>>>

@@

@@

@@

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(boot)}

\NormalTok{run\_sim\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
  \FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
\NormalTok{  mean.fun }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(d, i) \{}
\NormalTok{    d }\OtherTok{\textless{}{-}}\NormalTok{ X[i]}
    \FunctionTok{return}\NormalTok{ (}\FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(d), }\FunctionTok{sd}\NormalTok{(d)))}
\NormalTok{  \}}

\NormalTok{  sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{15}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{30}\NormalTok{, }\DecValTok{40}\NormalTok{, }\DecValTok{60}\NormalTok{, }\DecValTok{80}\NormalTok{, }\DecValTok{100}\NormalTok{)}
\NormalTok{  num\_sample\_sizes }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(sample\_sizes)}
\NormalTok{  master }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ num\_sample\_sizes, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}

  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{num\_sample\_sizes) \{}

\NormalTok{    norm\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
\NormalTok{    basic\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
\NormalTok{    student\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
\NormalTok{    percentile\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}
\NormalTok{    bca\_contains }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, sim\_reps)}

\NormalTok{    boot\_reps }\OtherTok{\textless{}{-}} \DecValTok{2000}
\NormalTok{    n }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes[i]}
\NormalTok{    true\_mean }\OtherTok{\textless{}{-}} \FunctionTok{exp}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{)}

    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{sim\_reps) \{}
\NormalTok{      X }\OtherTok{\textless{}{-}} \FunctionTok{rlnorm}\NormalTok{(n, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{)}
\NormalTok{      values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}

\NormalTok{      results }\OtherTok{\textless{}{-}} \FunctionTok{boot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ values, }\AttributeTok{statistic =}\NormalTok{ mean.fun, }\AttributeTok{R =}\NormalTok{ boot\_reps)}
\NormalTok{      results}
      \CommentTok{\#plot(results)}
\NormalTok{      ci }\OtherTok{\textless{}{-}} \FunctionTok{boot.ci}\NormalTok{(results, }\AttributeTok{type =} \StringTok{"all"}\NormalTok{)}

\NormalTok{      norm\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{2}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{normal[}\DecValTok{3}\NormalTok{]}
\NormalTok{      basic\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{basic[}\DecValTok{5}\NormalTok{]}
\NormalTok{      student\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{student[}\DecValTok{5}\NormalTok{]}
\NormalTok{      percentile\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{percent[}\DecValTok{5}\NormalTok{]}
\NormalTok{      bca\_contains[j] }\OtherTok{\textless{}{-}}\NormalTok{ true\_mean }\SpecialCharTok{\textgreater{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{4}\NormalTok{] }\SpecialCharTok{\&}\NormalTok{ true\_mean }\SpecialCharTok{\textless{}=}\NormalTok{ ci}\SpecialCharTok{$}\NormalTok{bca[}\DecValTok{5}\NormalTok{]}

\NormalTok{    \}}
